---
title: "RepData_PeerAssessment1"
author: "MegSchneider"
date: "Friday, February 13, 2015"
output: html_document
---

## Loading and preprocessing the data
First, load the data.

```{r}
data <- read.csv("activity.csv", header = TRUE, sep=",")
```

Process the data time strings into POSIX.
```{r}
date <- strptime(data$date, format="%Y-%m-%d")
```

Create a variable to include multiple observations in a day into a single day for data processing.

```{r}
simplifieddate <- vapply(date, FUN, simplify = TRUE, USE.NAMES = TRUE)
```

## What is mean total number of steps taken per day?

Create a histogram of total number of steps taken each day (ignoring missing values).

```{r}
histogram <- hist(data$steps)
```

Calculate and report the mean and median of total number of steps taken per day.

```{r}
bad <-x[!is.na(x)]
```

## What is the average daily activity pattern?

Create a time series plot (type = "1") of the 5 minute interval (x axis) and the average number of steps taken, averaged across all days on the y axis.

```{r}
bad <-x[!is.na(x)]
```

Calculate and report the number of missing values. (Total number of rows with NA)

```{r}
bad <-x[!is.na(x)]
```

## Imputing missing values

Use the BLANK strategy for filling in missing values of the dataset. (Mean/median of day, or mean for 5 minute interval)

```{r}
bad <-x[!is.na(x)]
```

Create a new dataset equal to original datset with missing data filled in.

```{r}
bad <-x[!is.na(x)]
```

Create a histogram now with total nmber of steps taken each day.

```{r}
bad <-x[!is.na(x)]
```

Calculate and report mean and median total number of steps taken per day.

```{r}
bad <-x[!is.na(x)]
```

From this, we can tell that these values DIFFER/ARE SIMILAR to the estimates from the first part of the assignment. Imputing missing data impacts the estimates of the total number of steps by ...

## Are there differences in activity patterns between weekdays and weekends?

Using the dataset with this filled-in missing values, create a new factor variable with two levels-"weekday" and "weekend" indicating whether a given date is a weekday or weekend day using weekdays().

```{r}
bad <-x[!is.na(x)]
```

Make a panel plot containing a time series plot (type = "1") of 5 minute interval (x axis) and average number of steps taken, averaged across all weekdays days OR weekend days (y axis). (README in github will show you how this works)
